Practical Machine Learning Project (Coursera)
========================================================

Using devices such as Jawbone Up, Nike FuelBand, and Fitbit it is now possible to collect a large amount of data about personal activity relatively inexpensively. These type of devices are part of the quantified self movement – a group of enthusiasts who take measurements about themselves regularly to improve their health, to find patterns in their behavior, or because they are tech geeks. One thing that people regularly do is quantify how much of a particular activity they do, but they rarely quantify how well they do it. In this project, your goal will be to use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants. They were asked to perform barbell lifts correctly and incorrectly in 5 different ways. More information is available from the website here: http://groupware.les.inf.puc-rio.br/har (see the section on the Weight Lifting Exercise Dataset). 

# Summary

goal: 
- to predict the manner in which people did the exercise ("classe" variable) using any other variables  

steps:
- use cross validation and out-of-sample error estimation
- build prediction models
- compare models
- predict 20 test cases

# Steps
```{r}
library(caret)
```

Load data sets
```{r cache=TRUE}
Train <- read.csv("pml-training.csv")
Test <- read.csv("pml-testing.csv")
length(Test)
```

Eliminate irrelevant variables (user_name, timestamps, window) and varibles with lot of *NA*s (here with all *NA* in Test set).
```{r cache=TRUE}
NAcols <- which(colSums(!is.na(Test))==0)
irrelevant.names <- c(1:7)
TrainN <- Train[,-c(irrelevant.names, NAcols)]
TestN <- Test[,-c(irrelevant.names, NAcols)]
length(TestN)
```
**Note:** the variable *cvtd_timestamp* may be useful if extract information about weekdays and time from it (as seen in previous Data Science courses).


Split the data  (70% for the training data set):
```{r cache=TRUE}
set.seed(23)
inTrain <- createDataPartition(TrainN$classe, p=0.7, list=FALSE)
trainTrainN <- TrainN[inTrain,]
testTrainN <- TrainN[-inTrain,]
```



# Build a Classification Tree

4-fold cross validation used
```{r cache=TRUE}
model.rpart <- train(classe ~ ., data=trainTrainN, method="rpart", 
                     trControl=trainControl(method="cv", number=4, repeats=2))
```
```{r}
plot(model.rpart$finalModel, uniform=TRUE, main="Classification Tree")
text(model.rpart$finalModel, use.n=TRUE, all=TRUE, cex=.8)
```

Predictions
```{r}
pred.rpart <- predict(model.rpart, testTrainN)
confusionMatrix(pred.rpart, testTrainN$classe)
```

# Build a Random Forest

4-fold cross validation used
```{r cache=TRUE}
set.seed(2015)
model.rf <- train(classe ~ ., data=trainTrainN, method="rf", 
                     trControl=trainControl(method="cv", number=4, repeats=2))
```
```{r}
plot(model.rf$finalModel)
```

Predictions
```{r}
pred.rf <- predict(model.rf, testTrainN)
confusionMatrix(pred.rf, testTrainN$classe)
```

# Out-of-sample error

Out-of-sample error can be estimated 1-Accuracy of cross validation.
Therefore it is:
- 51.89% for the Classification Tree
- 0.61% for the Random Forest

# Prediction

We use Random Forest (which having least estimated out-of-sample error) to make a prediction on the test set:

```{r}
pred <- predict(model.rf, TestN)
pred
```